Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-19 Paper.tex
Appendix list of symbols: only bigvee, plus zbMATH01748069 ref

Note that \mindifficulty is the difficulty of the genesis block. The effect of the difficulty parameter \homesteadmod on a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. \expdiffsymb results in the difficulty increasing every 10000 blocks. This is necessary to stabilise the time difference between blocks as  computation power becomes more efficient, with Moore's Law, although the rate of increase in computational efficiency has slowed down and may probably continue to slow down (\cite{THOMPSON200620}.

@@

>>>>

@@

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabularx}{\textwidth}{lcX}
\toprule
Symbol & Latex Command & Description \\
\midrule
\hypertarget{bigvee}{
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements (\cite{zbMATH01748069}).}\\
\bottomrule
\end{tabularx}
